Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
compare MFCC with scattering in ASC, cite Salamon 2015

\subsubsection*{MFCCs \vs scattering}
As shown in Figure, log-scattering coefficients consistently outperform $MFCCs$ over all folds of the DCASE 2013 private dataset.
The average accuracy

@@

\subsubsection*{Participation to the DCASE 2016 challenge}
In order to evaluate how general these results are, we have taken part in the acoustic scene classification task 2016 edition of the DCASE challenge.

>>>>

\subsubsection*{MFCCs \vs scattering}
As shown in Figure, scattering coefficients outperform MFCCs over all but one fold of the DCASE 2013 private dataset when applying early integration, and over all folds when applying late integration.
Not only the average accuracy is improved, but the variance between fold-wise accuracies is also reduced, \eg from $16\%$ to $7\%$ in the case of early integration.
This is in accordance with the previous results on similarity retrieval, as well as with other papers comparing mel-frequency coefficients with scattering coefficients on a variety of tasks, ranging from musical genre recognition \cite{Anden2014} to environmental sound classification \cite{Salamon2015}.

@@

\subsubsection*{Participation to the DCASE 2016 challenge}
In order to evaluate how general our findings are, we have taken part in the acoustic scene classification task 2016 edition of the DCASE challenge.
